Investigating Determinism of Physics Engines for usage in CAV and V\&V simulations

### 2019-12-12 paper_arxiv/1_Intro.tex
Added archives version but needs modifications

\noindent \IEEEPARstart{T}{}he evolution and inevitable implementation of connected and autonomous vehicles (CAVs) on roads is a delicate if not utterly fascinating subject.

>>>>

\noindent The evolution and inevitable implementation of connected and autonomous vehicles (CAVs) on roads is a delicate if not utterly fascinating subject.

### 2019-12-12 paper_arxiv/4_CaseStudy.tex
Added archives version but needs modifications

\begin{figure}[h] 
\label{TestsDiagrams}
  \centering
  \subfloat[]{\includegraphics[width=0.25\textwidth]{Other/Figures/TestCasesDiagram_a.pdf}\label{Test_a}}
  \subfloat[]{\includegraphics[width=0.25\textwidth]{Other/Figures/TestCasesDiagram_b.pdf}\label{Test_b}}
  \caption{Shows the setup of the different tests in Table \ref{TableOfExperiments} (a)Test IDs 1 to 4 (b)Test IDs 5 to 8.}
\end{figure}

@@

\begin{figure*}[h] 
  \centering
  \subfloat[]{\includegraphics[width=0.48\textwidth]{Other/Figures/CarsCollisionCG25.pdf}\label{CarsCollisionCG25}}
  \subfloat[]{\includegraphics[width=0.48\textwidth]{Other/Figures/CarsCollisionPrePost.pdf}\label{CarsCollisionPrePost}}
  \caption{Test ID 2 (a)Mean deviation vs simulation time for 25\% stress. (b)Pre and post collision mean deviation at different CPU+GPU stresses.}
\end{figure*}

\begin{figure*}[h] 
  \centering
  \subfloat[]{\includegraphics[width=0.48\textwidth]{Other/Figures/CarsPeopleCollsionsCG25.pdf}\label{CarsPeopleCollsionsCG25}}
  \subfloat[]{\includegraphics[width=0.48\textwidth]{Other/Figures/CarsPeopleCollisionPrePost.pdf}\label{CarsPeopleCollisionPrePost}}
  \caption{Test ID 4 (a)Mean deviation vs simulation time for 25\% stress. (b)Pre and post collision mean deviation at different CPU+GPU stresses.}
\end{figure*}

>>>>

\begin{figure}[h]
    \centering
    \begin{subfigure}{.24\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/TestCasesDiagram_a.pdf}
        \caption{}
        \label{Test_a}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/TestCasesDiagram_b.pdf}
        \caption{}
        \label{Test_b}
    \end{subfigure}
    \caption{Shows the setup of the different tests in Table \ref{TableOfExperiments} (a)Test IDs 1 to 4 (b)Test IDs 5 to 8.}
\end{figure}

@@

\begin{figure*}[h]
    \centering
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsCollisionCG25.pdf}
        \caption{}
        \label{CarsCollisionCG25}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsCollisionPrePost.pdf}
        \caption{}
        \label{CarsCollisionPrePost}
    \end{subfigure}
    \caption{Test ID 2 (a)Mean deviation vs simulation time for 25\% stress. (b)Pre and post collision mean deviation at different CPU+GPU stresses.}
\end{figure*}

\begin{figure*}[h]
    \centering
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsPeopleCollsionsCG25.pdf}
        \caption{}
        \label{CarsPeopleCollsionsCG25}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsPeopleCollisionPrePost.pdf}
        \caption{}
        \label{CarsPeopleCollisionPrePost}
    \end{subfigure}
    \caption{Test ID 4 (a)Mean deviation vs simulation time for 25\% stress. (b)Pre and post collision mean deviation at different CPU+GPU stresses.}
\end{figure*}
